s.function for 10 postcodes

### 2024-08-14 src/s_la_per_firm_corrected_10.Rmd
sum corrected

---
title: "s.function"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

library(tidyverse)
library(broom)
library(rprojroot)
#library(rgdal)
library(sf)
library(modelr)
#library(survival)
#library(rgeos)
library(spdep)
library(tidygeocoder)
# library(geosphere)
# library(raster)
library(rms)
library(stargazer)

@@

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]
```

@@

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = sum(n)) %>% # **********ATTENTION*********  
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

cities.sf <- bind_rows(cities.1, cities.2) %>% 
  st_as_sf(coords = c("long", "lat"), crs = 4326)
```
## S function estimation for all the country

@@

```{r}
df.country <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = sum(n)) %>% # it was n=n() **********ATTENTION*********  
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) %>% 
  left_join(firms) %>% 
  group_by(year) %>% 
  summarise(n = sum(n, na.rm = T),
            firms = sum(firms, na.rm = T)) %>% 
  mutate(n = n/firms) %>% 
  dplyr::select(-firms)

@@

# xmid = 2003.118
xmid.uk <- tidy(fit) %>% 
  filter(term=="xmid") %>% 
  dplyr::select(estimate) %>% as.numeric()

@@

path.out <- paste0(path, "/outputs/s/s_uk_per_firm.png")

@@

# plots
path.out <- paste0(path, "/outputs/s/s_lad_per_firm/lad_")

@@

```{r eval=F}
path.out <- paste0(path, "/outputs/s/s_la_per_firm.csv")

@@

```{r}
path.out <- paste0(path, "/outputs/s/speed_map.png")

@@

Change percentile in out.path and uncomment `mutate(alpha = ifelse(abs(diff_1st) > ...`

@@

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only95_av.png")

@@

  # ungroup() %>% summarise(q = quantile(abs(diff_1st), .05, na.rm = T))
  # q.95 = 253, q.9 = 214, q.1 = 11, q.05 = 3.75. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 253, .8, 0.1)) %>% 
  #mutate(alpha = ifelse(abs(diff_1st) <= 3.75, .8, 0.1)) %>%

>>>>

---
title: "s.function for 10 postcodes"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)
library(ggbump)
library(ggrepel)

@@

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]

```

@@

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = sum(n)) %>% # for multiple pc  **********ATTENTION*********
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

cities.sf <- bind_rows(cities.1, cities.2) %>% 
  st_as_sf(coords = c("long", "lat"), crs = 4326)
```

## S function estimation for all the country

@@

```{r}
df.country <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = sum(n)) %>% # for multiple pc  **********ATTENTION*********
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) %>% 
  left_join(firms) %>% 
  group_by(year) %>% 
  summarise(n = sum(n, na.rm = T),
            firms = sum(firms, na.rm = T)) %>% 
  mutate(n = n/firms) %>% 
  dplyr::select(-firms)

@@

# xmid = 2002.303
xmid.uk <- tidy(fit) %>% 
  filter(term=="xmid") %>% 
  dplyr::select(estimate) %>% as.numeric()

@@

path.out <- paste0(path, "/outputs/s/s_uk_per_firm_10.png")

@@

# plots
path.out <- paste0(path, "/outputs/s/s_lad_per_firm_10/lad_10_")

@@

```{r eval=F}
path.out <- paste0(path, "/outputs/s/s_la_per_firm_10.csv")

@@

```{r}
path.out <- paste0(path, "/outputs/s/speed_map_10.png")

@@

Change percentile in out.path and mutate(alpha = ifelse(abs(diff_1st)

@@

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only95_av_10.png")

@@

  # ungroup() %>% summarise(q = quantile(abs(diff_1st), .95, na.rm = T))
  # q.95 = 194.5, q.9 = 162.5, q.1 = 10.5, q.05 = 5. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 194.5, .8, 0.1)) %>% 
  #mutate(alpha = ifelse(abs(diff_1st) <= 5, .8, 0.1)) %>%
